Computing Entropies with Nested Sampling

### 2017-10-16 talk/ms.tex
Committing before going home
Edited one character :)
Moved some things around

@@

% New slide
\begin{frame}
\frametitle{Some entropies in Bayesian statistics}
Writing them in terms of parameters $\boldsymbol{\theta}$ and data
$d$, for Bayesian purposes.

\begin{enumerate}
\item Entropy of the prior for the parameters $H(\boldsymbol{\theta})$
\item Entropy of the conditional prior for the data $H(\boldsymbol{\theta} | d)$
\item Entropy of the posterior $H(\boldsymbol{\theta} | d)$
\item Entropy of the prior for the data $H(d)$
\end{enumerate}

Note: {\em conditional entropies} such as (2) and (3)
are defined using an expectation over the quantity conditioned upon.

@@

Mutual information:
\begin{align}
I(\boldsymbol{\theta}; d) &= H(\boldsymbol{\theta}) - H(\boldsymbol{\theta} | d).
\end{align}
This quantities dependence --- or more fundamentally,
relevance, or the potential for learning.

>>>>

% New slide
\begin{frame}
\frametitle{Some entropies in Bayesian statistics}
Written them in terms of parameters $\boldsymbol{\theta}$ and data
$d$, for Bayesian purposes.

\begin{enumerate}
\item<2-> Entropy of the prior for the parameters $H(\boldsymbol{\theta})$
\item<3-> Entropy of the conditional prior for the data $H(\boldsymbol{\theta} | d)$
\item<4-> Entropy of the posterior $H(\boldsymbol{\theta} | d)$
\item<5-> Entropy of the prior for the data $H(d)$
\end{enumerate}

@@

% New slide
\begin{frame}
\frametitle{Some entropies in Bayesian statistics}

\begin{block}{Remark}
{\em Conditional entropies} such as (2) and (3)
are defined using an expectation over the quantity conditioned upon.
\end{block}

@@

Mutual information:
\begin{align}
I(\boldsymbol{\theta}; d) &= H(\boldsymbol{\theta}) - H(\boldsymbol{\theta} | d).
\end{align}
This quantifies dependence --- or more fundamentally,
relevance, or the potential for learning.

{\tiny There are many other ways of expressing $I$.}
